Distribution of TADs

### 2019-05-08 Scripts/distribution_of_tads.Rmd
editted results script

tad_data <- tad_gm12878_10kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

gm12878_10kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_10kb_tabdist <- ggplot(tad_gm12878_10kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

tad_data <- tad_gm12878_25kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

gm12878_25kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_25kb_tabdist <- ggplot(tad_gm12878_25kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

tad_data <- tad_gm12878_50kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

gm12878_50kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_50kb_tabdist <- ggplot(tad_gm12878_50kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

tad_data <- tad_gm12878_100kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

gm12878_100kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_100kb_tabdist <- ggplot(tad_gm12878_100kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

tad_data <- tad_K562_10kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

K562_10kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

K562_10kb_tabdist <- ggplot(tad_K562_10kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

tad_data <- tad_K562_25kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

K562_25kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

K562_25kb_tabdist <- ggplot(tad_K562_25kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

tad_data <- tad_K562_50kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

K562_50kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

K562_50kb_tabdist <- ggplot(tad_K562_50kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

tad_data <- tad_K562_100kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

K562_100kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

K562_100kb_tabdist <- ggplot(tad_K562_100kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

# Plots

```{r}
figure <- ggarrange(gm12878_10kb_tabnum,gm12878_10kb_tabdist,
                    gm12878_25kb_tabnum,gm12878_25kb_tabdist,
                    gm12878_50kb_tabnum,gm12878_50kb_tabdist,
                    gm12878_100kb_tabnum,gm12878_100kb_tabdist,
                    ncol=2,nrow=4,
                    common.legend = TRUE,
                    legend="right",
                    labels = c("A", "","B", "","C", "","D", ""),
                    font.label = list(size=20))

figure <- ggarrange(K562_10kb_tabnum,K562_10kb_tabdist,
                    K562_25kb_tabnum,K562_25kb_tabdist,
                    K562_50kb_tabnum,K562_50kb_tabdist,
                    K562_100kb_tabnum,K562_100kb_tabdist,
                    ncol=2,nrow=4,
                    common.legend = TRUE,
                    legend="right",
                    labels = "AUTO",
                    font.label = list(size=20))
```

# Creating Table of Summaraies

```{r}
tad_gm12878_10kb$CL <- "GM12878"
tad_gm12878_25kb$CL <- "GM12878"
tad_gm12878_50kb$CL <- "GM12878"
tad_gm12878_100kb$CL <- "GM12878"
tad_K562_10kb$CL <- "K562"
tad_K562_25kb$CL <- "K562"
tad_K562_50kb$CL <- "K562"
tad_K562_100kb$CL <- "K562"

tad_data_summaries <- rbind.data.frame(aggregate(tad_gm12878_10kb$Length, by=list(tad_gm12878_10kb$V1), FUN=summary),
                 aggregate(tad_gm12878_25kb$Length, by=list(tad_gm12878_25kb$V1), FUN=summary),
                 aggregate(tad_gm12878_50kb$Length, by=list(tad_gm12878_50kb$V1), FUN=summary),
                 aggregate(tad_gm12878_100kb$Length, by=list(tad_gm12878_100kb$V1), FUN=summary),
                 aggregate(tad_K562_10kb$Length, by=list(tad_K562_10kb$V1), FUN=summary),
                 aggregate(tad_K562_25kb$Length, by=list(tad_K562_25kb$V1), FUN=summary),
                 aggregate(tad_K562_50kb$Length, by=list(tad_K562_50kb$V1), FUN=summary),
                 aggregate(tad_K562_100kb$Length, by=list(tad_K562_100kb$V1), FUN=summary))

#chr 9 for k562 at 10 kb has no tad boundaries

tad_data_summaries$CL <- c(rep("GM12878", 22*4), rep("K562", 22*4-1))
tad_data_summaries$Resolution <- c(rep("10 kb", 22),rep("25 kb", 22),rep("50 kb", 22),rep("100 kb", 22),
                                   rep("10 kb", 21),rep("25 kb", 22),rep("50 kb", 22),rep("100 kb", 22))

write.csv(tad_data_summaries, "C:/Users/stili/Downloads/tad_data_summaries.csv")
```

>>>>

tad_data_gm12878_10kb <- tad_gm12878_10kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1),
            Length = mean(Length))

@@

tad_data_gm12878_25kb <- tad_gm12878_25kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1),
            Length = mean(Length))

@@

tad_data_gm12878_50kb <- tad_gm12878_50kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1),
            Length = mean(Length))

@@

tad_data_gm12878_100kb <- tad_gm12878_100kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1),
            Length = mean(Length))

@@

tad_data_K562_10kb <- tad_K562_10kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1),
            Length = mean(Length))

@@

tad_data_K562_25kb <- tad_K562_25kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1),
            Length = mean(Length))

@@

tad_data_K562_50kb <- tad_K562_50kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1),
            Length = mean(Length))

@@

tad_data_K562_100kb <- tad_K562_100kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1),
            Length = mean(Length))

@@

# Tables

```{r}
combined <- rbind.data.frame(tad_data_gm12878_10kb,
                             tad_data_gm12878_25kb,
                             tad_data_gm12878_50kb,
                             tad_data_gm12878_100kb,
                             tad_data_K562_10kb,
                             tad_data_K562_25kb,
                             tad_data_K562_50kb,
                             tad_data_K562_100kb)

combined <- combined[-which(combined$V1==9),]
combined$V1 <- factor(combined$V1)

combined$CL <- c(rep("GM12878", 84), rep("K562", 84))
combined$Resolution <- c(rep("10 kb", 21),
                         rep("25 kb", 21),
                         rep("50 kb", 21),
                         rep("100 kb", 21),
                         rep("10 kb", 21),
                         rep("25 kb", 21),
                         rep("50 kb", 21),
                         rep("100 kb", 21))
combined$CL <- factor(combined$CL)
combined$Resolution <- factor(combined$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

summarytab <- combined %>% 
  group_by(CL, Resolution) %>% 
  summarise(AveNumber = mean(Count),
            SDNumber = sd(Count),
            AveLength = mean(Length),
            SDLength = sd(Length))
summarytab[,3:6] <- round(summarytab[,3:6], 1)
```
